Cover letter for the original IJRR submission

### 2017-10-09 reviews_tro/reviewer_response.tex

\quot{
p.6 six fingered hand is slightly misleading, since no rolling (as fully admitted in the text). I'd just cut this? \\
p.9 Not sure if Fig. 14 is worth including. It looks like its just Fig. 9 from the ISRR paper (?) [20], and there is still no ``full solution'' here -
 just an illustration of potential future work. 
 (At a minimum, the figure/solution should probably be referenced as having already appeared in the previous ISSR paper?)
}

\as{As also suggested by reviewer 4, we removed the references to the results of the previous work [20], including those.}\done

\quot{
p.8– somehow, “Table II” doesn’t appear until after “Table IV” – which is a frustrating choice for latex to make. Not sure what you can do to change that, but it would be preferable to have tables (and figures) appear in the correct order.
}

\as{We reorganized the paper such that the Tables appears in the right place, by inverting the Computation times and success rates paragraphs. The order of appearance of the Tables thus remains
the same, but the numbering is correct, and in agreement with the order of referencement in the text.}\done

### 2017-10-09 body/results.tex
correct table order

% \subsubsection*{Truck egress (Figure~\ref{res_truck_pres} and Figure~\ref{res_truck_bd}) -- Humanoid and insectoid robots.}
%\subsubsection*{Truck egress -- Humanoid and insectoid robots (Figure~\ref{res_truck_bd}).}
\subsubsection{HRP-2 -- Staircase with high steps (Figure~\ref{fig:stair_robust})}

\begin{figure}
  \centering
  \includegraphics[width=1\linewidth]{figures/stair}
  \caption{
           HRP-2 in the stair climbing scenario. }
		   \label{fig:stair_robust}
\end{figure}

@@

\begin{table*}
\centering
\footnotesize
\begin{tabular}{ >{\centering\arraybackslash}m{37pt} | >{\centering\arraybackslash}m{57pt} | >{\centering\arraybackslash}m{65pt} | >{\centering\arraybackslash}m{70pt} | >{\centering\arraybackslash}m{73pt} | >{\centering\arraybackslash}m{80pt} | >{\centering\arraybackslash}m{10pt}}
  Scenario (nb steps) &  Complete guide generation (ms) & Static equilibrium (ms) & Collision (ms) & Inverse Kinematics (ms) & Total generation time (ms) & Time per step (ms)\\
 \hline
   Stairs (18) 	& 5 -- \textbf{6} --  18 		 & 13 --  \textbf{32} -- 329   	& 1 --  \textbf{4} -- 38 & 26 --  \textbf{127} -- 1345 & 92 --  \textbf{261} -- 2174 & \textbf{15} \\
   Standing (24)& 65 -- \textbf{1086} --  5227   & 27 --  \textbf{144} -- 338   & 2 --  \textbf{12} -- 37 & 144 --  \textbf{1046} -- 2374 & 371 --  \textbf{2257} -- 7671 & \textbf{94}  \\
   Car (86)& 320 -- \textbf{6971} --  44002 & 409 --  \textbf{1766} -- 14752   	& 297 -- \textbf{1187} -- 8483 & 3154 --  \textbf{15323} -- 165541 & 5834 --  \textbf{31391} -- 281000 & \textbf{365}\\
   Rubble (82)& 37 -- \textbf{573} --  1685 & 583 --  \textbf{2714} -- 9459 & 491 --  \textbf{1971} -- 6273 & 269 --  \textbf{706} -- 3118 & 1811 --  \textbf{7195} -- 23241 & \textbf{86} \\
   Race (134)& 14 -- \textbf{51} --  125 & 455 --  \textbf{1359} -- 21045   & 397 --  \textbf{923} -- 9924 & 228 --  \textbf{471} -- 5415 & 1436 --  \textbf{3343} -- 41446 & \textbf{25}
 \end{tabular}
\caption{minimum, \textbf{average} and worst time (in ms) spent in the generation process for each scenario and each critical part of the generation process (not all parts are timed,
thus the average total computation time is higher than the sum of each part). The last
column indicates the average time necessary to compute one contact transition. The Collision column times includes the (negligeable) octree intersection operation necessary to retrieve the candidate samples.}
\label{tab:requestime}
\quad
\end{table*}

@@

@@

These results confirm that our approach provides a satisfying compromise between completeness and efficiency, thus enabling online planning
while controlling the robot. Indeed, when the contact planning fails, it fails rapidly. This allows us to rapidly re-plan with a reasonable chance of success.
The most efficient (and immediate) approach to obtain a valid contact plan as fast as possible would be to launch in parallel several instances of the planner (our current implementation is single-threaded) and to use any successful result as a plan for solver $\mathcal{P}_3$.

>>>>

% \subsubsection*{Truck egress (Figure~\ref{res_truck_pres} and Figure~\ref{res_truck_bd}) -- Humanoid and insectoid robots.}
%\subsubsection*{Truck egress -- Humanoid and insectoid robots (Figure~\ref{res_truck_bd}).}
\subsubsection{HRP-2 -- Staircase with high steps (Figure~\ref{fig:stair_robust})}
\newcommand{\widthValue}{0.13\linewidth}

\begin{figure*}[h!t!]
  \begin{center}
  \includegraphics[trim={7.0cm 0.0cm 20.0cm 0.0cm}, clip, width=\widthValue]
    {./video/stairclimbing1.jpeg}
  \includegraphics[trim={7.0cm 0.0cm 20.0cm 0.0cm}, clip, width=\widthValue]
    {./video/stairclimbing2.jpeg}
  \includegraphics[trim={7.0cm 0.0cm 20.0cm 0.0cm}, clip, width=\widthValue]
    {./video/stairclimbing3.jpeg}
  \includegraphics[trim={7.0cm 0.0cm 20.0cm 0.0cm}, clip, width=\widthValue]
    {./video/stairclimbing4.jpeg}
  \includegraphics[trim={7.0cm 0.0cm 20.0cm 0.0cm}, clip, width=\widthValue]
    {./video/stairclimbing5.jpeg}
  \includegraphics[trim={7.0cm 0.0cm 20.0cm 0.0cm}, clip, width=\widthValue]
    {./video/stairclimbing6.jpeg}
  \includegraphics[trim={7.0cm 0.0cm 20.0cm 0.0cm}, clip, width=\widthValue]
    {./video/stairclimbing7.jpeg}
  \caption{
           HRP-2 in the stair climbing scenario. }
		   \label{fig:stair_robust}
  \label{fig:moviepicture2}
  \end{center}
  \vspace{-0.5cm}
\end{figure*}

%~ \begin{figure}
  %~ \centering
  %~ \includegraphics[width=1\linewidth]{figures/stair}
  %~ \caption{
           %~ HRP-2 in the stair climbing scenario. }
		   %~ \label{fig:stair_robust}
%~ \end{figure}

@@

@@

\begin{table*}[b!t!p!]
\centering
\footnotesize
\begin{tabular}{ >{\centering\arraybackslash}m{37pt} | >{\centering\arraybackslash}m{57pt} | >{\centering\arraybackslash}m{65pt} | >{\centering\arraybackslash}m{70pt} | >{\centering\arraybackslash}m{73pt} | >{\centering\arraybackslash}m{80pt} | >{\centering\arraybackslash}m{10pt}}
  Scenario (nb steps) &  Complete guide generation (ms) & Static equilibrium (ms) & Collision (ms) & Inverse Kinematics (ms) & Total generation time (ms) & Time per step (ms)\\
 \hline
   Stairs (18) 	& 5 -- \textbf{6} --  18 		 & 13 --  \textbf{32} -- 329   	& 1 --  \textbf{4} -- 38 & 26 --  \textbf{127} -- 1345 & 92 --  \textbf{261} -- 2174 & \textbf{15} \\
   Standing (24)& 65 -- \textbf{1086} --  5227   & 27 --  \textbf{144} -- 338   & 2 --  \textbf{12} -- 37 & 144 --  \textbf{1046} -- 2374 & 371 --  \textbf{2257} -- 7671 & \textbf{94}  \\
   Car (86)& 320 -- \textbf{6971} --  44002 & 409 --  \textbf{1766} -- 14752   	& 297 -- \textbf{1187} -- 8483 & 3154 --  \textbf{15323} -- 165541 & 5834 --  \textbf{31391} -- 281000 & \textbf{365}\\
   Rubble (82)& 37 -- \textbf{573} --  1685 & 583 --  \textbf{2714} -- 9459 & 491 --  \textbf{1971} -- 6273 & 269 --  \textbf{706} -- 3118 & 1811 --  \textbf{7195} -- 23241 & \textbf{86} \\
   Race (134)& 14 -- \textbf{51} --  125 & 455 --  \textbf{1359} -- 21045   & 397 --  \textbf{923} -- 9924 & 228 --  \textbf{471} -- 5415 & 1436 --  \textbf{3343} -- 41446 & \textbf{25}
 \end{tabular}
\caption{minimum, \textbf{average} and worst time (in ms) spent in the generation process for each scenario and each critical part of the generation process (not all parts are timed,
thus the average total computation time is higher than the sum of each part). The last
column indicates the average time necessary to compute one contact transition. The Collision column times includes the (negligeable) octree intersection operation necessary to retrieve the candidate samples.}
\label{tab:requestime}
\quad
\end{table*}

@@

\subsubsection*{Conclusion}
These results confirm that our approach provides a satisfying compromise between completeness and efficiency, thus enabling online planning
while controlling the robot. Indeed, when the contact planning fails, it fails rapidly. This allows us to rapidly re-plan with a reasonable chance of success.
The most efficient (and immediate) approach to obtain a valid contact plan as fast as possible would be to launch in parallel several instances of the planner (our current implementation is single-threaded) and to use any successful result as a plan for solver $\mathcal{P}_3$.
